Trans-dimensional Bayesian Inference and Nested Sampling

### 2014-08-09 Documents/Talk/content.tex
Slide placeholders
Various work on the introductory slides

\begin{frame}[t]{Bayesian Inference 101}
Probabilities describe degrees of plausibility

Uncertain quantities described by probability distributions

@@

>>>>

\begin{frame}[t]{Bayesian Inference 101}
Bayesian Inference is a unified framework for solving inference problems.
We need the following ingredients:

\begin{itemize}
\setlength{\itemsep}{20pt}
\item A {\bf hypothesis space} describing the set of possible answers to our
question (``parameter space'' in fitting is the same concept).
\item A {\bf prior distribution} $p(\theta)$ describing how plausible
each of the possible solutions is, not taking into account the data.
\item A {\bf sampling distribution} $p(D | \theta)$ describing our knowledge
about the connection between the parameters and the data.
\end{itemize}

@@

\begin{frame}[t]{Bayesian Inference 101}
The data helps us by changing our prior distribution to the {\bf posterior
distribution}, given by
\begin{eqnarray}
p(\theta | D) &=& \frac{p(\theta) p(D|\theta)}{p(D)}
\end{eqnarray}
where the denominator is the normalisation constant, usually called either
the {\bf marginal likelihood} or the {\bf evidence}.
\begin{eqnarray}
p(D) &=& \int p(\theta)p(D|\theta) \, d\theta.
\end{eqnarray}

\begin{frame}[t]{Bayesian Computation}
To explore the posterior distribution, the Metropolis algorithm is a standard
technique.

\begin{frame}[t]{Birth and Death}
For problems of unknown dimensionality, the hypothesis space is the union
of several fixed-dimension hypothesis spaces.
